---
output:
  html_document:
    bibliography: bibtex
    highlight: tango
    keep_md: yes
    theme: spacelab
---

### Last Update

```{r}
Sys.time()
```


### Data Set

The used data set was derived from an own account and own comparisons by the use of Alexa.com Competitive Intelligence metrics.

The presented forecasts relate to the Alexa Time on Site metric.

Related websites:

* [Amnesty International][1]

* [American Red Cross][2] 

* [PETA][3] 


***

### Notices

This application is primarily a demo to show what is possible. 

In case of any questions related to this application, feel free to write [me a mail.][4]

***

### Used R Packages

```{r, eval=FALSE}
library(graph)
library(twitteR)
library(NLP)
library(tm)
library(shinyIncubator)
library(grid)
library(pvclust)
library(Rgraphviz)
library(qdapTools)
library(qdapRegex)
library(magrittr)
library(wordcloud)
library(RColorBrewer)
library(ggplot2)
library(RCurl)
library(bitops)
library(shinyapps)
library(BH)
library(qdap)
library(SnowballC)
library(slam)
library(RWeka)
library(rJava) 
library(RWekajars)
library(memoise)
library(devtools)
library(rjson)
library(bit64)
library(httr)
library(plyr)
```

***

### Last Session Info

```{r}
sessionInfo()
```



[1]: https://twitter.com/amnesty "Amnesty Twitter Account"

[2]: https://twitter.com/RedCross "Red Cross Twitter Account"

[3]: https://twitter.com/peta "PETA Twitter Account"

[4]: http://nierhoff.info/#contact "Contact"

***
